Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-08 Paperfolder/Paperfolder.Rmd
Updated intro started

---
title: Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
  - short: HR
    long: hazard ratio
  - short: sd
    long: standard deviation
  - short: CrI
    long: credible interval
output: rticles::mdpi_article
---

<!-- # Version -->

<!-- This Rmd-skeleton uses the mdpi Latex template published 2019/02.  -->
<!-- However, the official template gets more frequently updated than the 'rticles' -->
<!-- package. Therefore, please make sure prior to paper submission, that you're  -->
<!-- using the most recent .cls, .tex and .bst files  -->
<!-- (available [here](http://www.mdpi.com/authors/latex)). -->

@@

<!-- The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. -->

>>>>

---
title: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: FFQ
    long: Food Frequency Questionnaire
  - short: MCMC
    long: Markov Chain Monte Carlo
  - short: JAGS
    long: Just Another Gibbs Samplers
  - short: HR
    long: hazard ratio
  - short: sd
    long: standard deviation
  - short: CrI
    long: credible interval
output: rticles::mdpi_article
---

@@

Dairy food, especially milk has been recommended to reduce stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. More intuitive interpretation for a decreasing risk would be possible if we were able to compute the exact probability for people who had milk intake may had lower hazard of dying from stroke compared with those who never drank milk at all. For general public/media reporting, concept of hazard in epidemiological studies could still sometimes be challenging to be understood or misinterpreted since it should be formally defined as the probability of the occurrence of an event at a given time point. Usually, authors of epidemiological papers would tend to use "risk" instead of "hazard" or interchangeably. However, it would still possibly be mixed up with "risk" that only contain pure "probability" without a point or a period of time in cross-sectional settings. For better understanding and interpretation of the data that researchers endeavored to collect, statistical literature have provided plenty of choices that could help us better communicate with each other.

### 2020-07-08 Paperfolder/Paperfolder.tex
Updated intro started

%=================================================================
% Full title of the paper (Capitalized)
\Title{Milk intake and risk of mortality risk in the Japan Collaborative
Cohort Study - a Bayesian survival analysis}

@@

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Milk intake and stroke mortality in the Japan Collaborative
Cohort Study - a Bayesian survival analysis}

@@

Dairy food, especially milk has been recommended to reduce stroke risk
by nearly 7\% for each 200 g increment of daily consumption
\citep{DeGoede2016}. More intuitive interpretation for a decreasing risk
would be possible if we were able to compute the exact probability for
people who had milk intake may had lower hazard of dying from stroke
compared with those who never drank milk at all. For general
public/media reporting, concept of hazard in epidemiological studies
could still sometimes be challenging to be understood or misinterpreted
since it should be formally defined as the probability of the occurrence
of an event at a given time point. Usually, authors of epidemiological
papers would tend to use ``risk'' instead of ``hazard'' or
interchangeably. However, it would still possibly be mixed up with
``risk'' that only contain pure ``probability'' without a point or a
period of time in cross-sectional settings. For better understanding and
interpretation of the data that researchers endeavored to collect,
statistical literature have provided plenty of choices that could help
us better communicate with each other.
